\begin{center}
{\Huge \bf{Acknowledgement}\vskip 0.2in}
\end{center}

I, student of Guru Nanak Dev Engineering College, Ludhiana, have taken efforts in this project.
However, it would not have been possible without the kind support and help of many individuals
and organizations. I would like to extend my sincere thanks to all of them.\\

The author is highly grateful to Dr. Sehijpal Singh, Principal, Guru Nanak Dev Engineering College, Ludhiana for providing him with the opportunity to carry out his two Months training at Testing and Consultancy Cell, Guru Nanak Dev Engineering College, two months training at Technocampus, Ludhiana and two months training at Numitech, Ludhiana .\\

The author would like to wholeheartedly thank Dr. H.S. Rai Dean, Testing and Consultancy Cell, Guru Nanak Dev Engineering College, Ludhiana who is a vast sea of knowledge, who introduced me to open street map and without whose constant and never ending support and motivation, it would never have been possible to complete the project and other assignments so efficiently and effectively.\\
I would like to express a deep sense of gratitude and thanks profusely to Mr. Gurnoor Singh who made 3d map, he helped me throughout the project and we were able to complete our project. I express gratitude to other faculty members of Information Technology department of GNDEC for their intellectual support throughout the course of this work.\\

I would like to express a deep sense of gratitude and thanks profusely to Mrs. Gagandeep Kaur, without her wise counsel and able guidance, it would have been impossible to complete the application in this manner. I am highly indebted to my mentor for her guidance and constant supervision as well as for providing necessary information regarding the project & also for their support in completing the project.I would like to express my gratitude towards my mentor for her kind co-operation and encouragement which help me in completion of this project.\\


\vskip 1.0cm 
\noindent Abhinav Handa 



